Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-02 tex/A.tex
Add the APM
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\documentclass[11pt, a4paper]{report}
\usepackage[a4paper]{geometry}

% Packages
\usepackage{tipa}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage[ruled,boxed]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{tcolorbox}
\usepackage{amsmath}
\usepackage{mathtools}

@@

    \chapter{The Argennon Smart Contract Execution Environment}\label{ch:AVM}
    \note{This chapter is outdated and does not include CI proofs. Currently a new version is being rewritten.}
    \input{sections/avm}

@@

    \section{Normal Mode}\label{sec:normal-mode}
    Unlike conventional blockchains, Argennon does not use a P2P network architecture. Instead, it uses a
    client-server topology, based on a permission-less list of ZK-EDB servers. ZK-EDB servers are a
    crucial part of the Argennon ecosystem, and they form the backbone of the Argennon networking layer.
    \note{not yet written...}

>>>>

\documentclass[11pt, a4paper]{report}

% Packages
\usepackage{tipa}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage[ruled,boxed]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{tcolorbox}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[a4paper]{geometry}
\usepackage{tikz}

@@

    \chapter{The Argennon Smart Contract Execution Environment}\label{ch:AscEE}
    \input{sections/avm}

    \chapter{The Argennon Prover Machine}\label{ch:APM}
    \input{sections/apm}

@@

    \section{Normal Mode}\label{sec:normal-mode}
    Unlike conventional blockchains, Argennon does not use a P2P network architecture. Instead, it uses a
    client-server topology, based on a permission-less network of PVC servers. PVC servers are a
    crucial part of the Argennon ecosystem, and they form the backbone of the Argennon networking layer.
    \note{not yet written...}

### 2022-09-02 tex/sections/avm.tex
Add the APM
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Smart Contract Execution
Environment (AscEE) is an abstract execution environment for executing Argennon smarts contracts (a.k.a\ Argennon
applications) in a safe and secure environment. An Argennon application essentially is an HTTP server whose state is
kept in the Argennon blockchain and its logic is described using an Argennon Standard Representation (ASR).

An Argennon Standard Representation (ASR) is a programming language for describing Argennon applications, optimized
for the architecture and properties of the Argennon platform.
Argennon supports two standard representations: One is a high level text based representation which needs
costly compilation before being executed on a hardware machine. The other is a low level binary representation which
usually can be executed, with minimal pre-processing, by a JIT compiler or an emulator. The high level
language is intended for preserving the high level information of the application logic to facilitate
platform specific compiler optimization at a host machine. The low level language, on the oder hand, is designed for
efficient direct execution of applications that are not frequently used and do not benefit from compiler optimizations.

The state of an Argennon application is stored in byte addressable finite arrays of memory called
\emph{heap chunks}. An application may have several heap chunks with different sizes, and can remove or
resize its heap chunks or allocate new chunks. Every chunk belongs to exactly one application and can only be modified
by its owner. In addition to heap chunks, every application has an amount of non-persistent local memory for
storing temporary data.

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data for executing requests are retrieved from the Argennon cloud, the cryptographic proofs are verified and the
helper data structures for next steps are constructed. This step is
designed in a way that can be done fully in parallel for each request without any risk of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution DAG} data
structure and in the final step, the requests are executed using this data structure.

@@

The Argennon Smart Contract Execution Environment can be seen as a machine for executing Argennon applications to
fulfill HTTP requests, produce their HTTP responses and update related heap chunks. The execution of requests can be
considered sequential\footnote{Actually requests are executed in parallel but by performing data dependency analysis the
result is guaranteed to be identical with sequential execution of requests.} and each request has a separate
\emph{execution session}. Therefore, an execution
session is a separate session of executing smart contract's code in order to fulfill an \emph{external} HTTP request.
External requests are requests that are not made by other Argennon applications.

The state of an execution session will be
destroyed at the end of the session and only the state of heap chunks is preserved. If a session fails and does not
complete normally, it will not have any effect on any heap chunks.

During an execution session an application can make \emph{internal} HTTP requests to other applications. Those
requests will not start a new execution session and will be executed within the current session. In AscEE making an
HTTP request to an application is similar to a function invocation, and for that reason, we also refer to them as
application calls.

The AscEE is designed based on \emph{optional decoupling principle}. When an application makes a request to another
application, optionally it can choose to be decoupled from the called application. That would mean the called
application could not affect its caller's state by reentrancy, or could not abort the session by using excessive
resources or performing illegal operations.

@@

\section{Heap Chunks}\label{heap}

The persistent data of an Argennon application is stored in continuous finite
arrays of bytes, called heap chunks. An application may have several heap chunks
with different sizes, and can remove or
resize its chunks or allocate new chunks. Every chunk belongs to exactly one application. Only the owner application can
modify a chunk but there is no restrictions for reading a chunk\footnote{The reason behind this type of access
control design is the fact that smart contract
code is usually immutable. That means if a smart contract does not implement a
getter mechanism for some parts of its internal data, this functionality can never
be added later, and despite the internal data is publicly available, there will be no
way for other smart contracts to use this data on-chain.}.

When an application allocates a new heap chunk, the identifier of the new chunk is not generated by
the AscEE. Instead, the application can choose an identifier itself, provided it has a correct format. This
is an important feature of the AscEE heap, which allows applications to use the AscEE heap as a dictionary
data structure\footnote{also called a map.}.
Since the \texttt{chunkID} is a prefix code, any application has its own identifier space, and an application
can easily find unique identifiers for its chunks.

\subsection{Chunk Resizing}\label{subsec:ch-resize}

At the start of executing requests of a block, a validator can consider two values for every
heap chunk, the size: \texttt{chunkSize} and a size upper bound: \texttt{sizeUpperBound}. The value of
\texttt{chunkSize} can be determined uniquely at the start of
every execution session, and it may be updated during the session by the owner application. On the other hand,
the value of \texttt{sizeUpperBound} is determined and fixed for each block and is proposed by the block
proposer. This value indicates the upper bound of \texttt{chunkSize} during the execution of
requests of the block, and it can be used by the validator for safe memory allocation.

The value of \texttt{chunkSize}, can be modified during an execution session. However, the new size values can only be
increasing or decreasing. More precisely, if a request declares that it wants to expand (shrink) a chunk, it can only
increase (decrease) the value of \texttt{chunkSize} and any specified value during the execution
session, needs to be greater (smaller) than the previous value of the chunk's size. Any request that wants to expand
(shrink) a chunk needs to specify a max size (min size). The value of \texttt{chunkSize} can not be set higher
(lower) than this value.

The value of \texttt{chunkSize} at the end of an execution session will determine if a memory location at an
offset is persistent or not: Offsets lower than the chunk size are persistent, and higher offsets are not.
Non-persistent locations will be re-initialized with zero at the start of every execution session.

Usually an application should not have any assumption about the content of memory locations that are outside the chunk.
While these locations are zero initialized at the start of every execution session, it should be noted that multiple
invocations of an application may occur in a single execution session, and if one of them modifies a location outside
the chunk, the changes can be seen by next invocations.

There is no way for an application to query \texttt{sizeUpperBound} of a chunk. As a result, for an application,
accessing offsets higher than \texttt{chunkSize} results in undefined behaviour, while the behaviour is well-defined
in the view of validators.
This enables validators to determine the validity of an offset at the start of the block validation in a parallelized
preprocessing phase without actually executing requests.

\subsection{Access Blocks}\label{subsec:access-blocks}

Memory locations inside a chunk can only be accessed through access blocks. An access block is an access interval
defined on a chunk, which determines the accessible memory locations inside the chunk. Each access block has an offset
and a size. Multiple access blocks can be defined on a single chunk, but they must be non overlapping.
Access blocks are byte addressable and may have different access types:

\begin{itemize}
    \item \texttt{check\_only}: only allows check operations. These operations query the persistence
    status of a memory location.
    \item \texttt{read\_only}: only allows read and check operations.
    \item \texttt{writable}: allows reading and writing.
    \item \texttt{additive}: only allows additive operations. These operations are addition-like operations without
    any overflow checking. These operations must be associative and commutative. Note that the content of
    these access blocks cannot be read.
\end{itemize}

Chunks and access blocks have different purposes. Chunks are intended for simplifying proof checking of the data
stored in the Argennon cloud\footnote{Note that
the Argennon cloud uses cryptographic accumulators for preserving data integrity.} and access blocks are
required for better parallelization of the request execution. An application should put the data needed for
validating a single block in the same chunk and the data needed in a single execution session in the same access block.

@@

\section{Authorizing Operations}\label{sec:authorizing-operations}

In blockchain applications, we usually need to authorize certain operations. For example, for sending an asset
from a user to another user, first we need to make sure that the sender has authorized this operation.

The AscEE uses \emph{Authenticated Message Passing} for authorizing operations. In this method, every execution
session has a set of authenticated messages, and those messages are \textbf{explicitly} passed in requests to
applications for authorizing operations. These messages act exactly like digital signatures and applications can
ensure that they are issued by specific accounts. The only difference is that the process of message authentication
is performed by the AscEE internally and is not performed by the application. For accounts, the AscEE uses digital
signatures to authenticate messages. Signatures for each request can be validated in parallel during the
preprocessing step of the block validation, and any type of
cryptographic signature scheme can be used. For example, we could use BLS aggregate signatures to authenticate all
messages of a block of the blockchain in bulk.

Moreover, applications can use built-in functions of the AscEE to generate authenticated messages in run-time.
This enables an application to authorize operations for another application even if it is not calling that
application directly.

In addition to authenticated messages, the AscEE provides a set of
cryptographic functions for validating signatures and cryptographic entities. By using these functions and
passing cryptographic signatures as parameters to methods, a programmer, having users' public keys, can implement
the required logic for authorizing operations.

Authorization by explicit authenticated messages and signatures eliminates the need for approval mechanisms or call back
patterns in Argennon.

\note{The AscEE has no instructions for issuing cryptographic signatures.}

@@

The Argennon Smart Contract Execution Environment provides optional low level reentrancy protection by providing low
level \emph{entrance locks}. When an application acquires an entrance lock it cannot acquire that lock again and trying
to do so will result in a revert. The entrance lock of an application will be released when the application explicitly
releases its lock or when the call that had acquired that lock completes.

@@

\section{Resource Management}\label{sec:res-man}

Completing an execution session requires computational resources. The amount of resources used by an execution session
should be monitored and managed, otherwise a malicious user would be able to easily spam and exhaust resources of the
execution environment.

In most consensus protocols, we can assume that the block proposer has enough incentive to filter out transactions
that spam run-time resources. Here by a run-time resource, we mean a resource that at run-time, a limited amount
of it is available, but its surplus can not be stored for later use. Execution time and local memory are
examples of such a resource but permanent storage is not.

If a proposed block contains many transactions which need a lot of run-time resources, validators would not
be able to validate all transactions in a timely manner. Consequently, they may decide to reject the block or if they
spend enough resources, the confirmation of that block could take more than usual. Longer block time is not
favoured by block proposers, because it means less throughput of the system which usually means less overall rewards
for them. In the Argennon protocol the management of run-time resources, is left to the block proposer.

Resource usage can be measured per session or per application call. Obviously per session measurement is
easier and more efficient. However, when we measure resources per session if
a session violates its resource caps, determining the point of failure may require precise and error-free resource
measurement. For example, assume that a session containing an application call
violates a 2 milliseconds execution time cap. If in the caller's code, the call happens exactly after 2 milliseconds,
a small fluctuation in the execution time measurement can
change the point of failure between the called and the caller application. Note that for implementing optional
decoupling principle in Argennon, we need to determine the
exact application call which has failed in a call chain, and this fluctuation introduces a nondeterministic
behaviour which could make block validation impossible. That's why we need per application call
resource management sometimes. If we define the resource caps per application call and
perform our measurements for each application call separately, by using caps that are larger than the measurement
error, errors in the measurements would not change the point of failure in the call chain.

The AscEE has two types of execution sessions: \emph{optimistic} and \emph{monitored}. Resource usage of an optimistic
session is always measured per session and \textbf{default} pre-defined resource caps are used. On the other hand, for a
monitored session, resources that can not be measured precisely are measured per application call and their caps are
determined per application call by the external HTTP request (i.e.\ transaction). The block proposer decides the
type of the execution session for each transaction.

Different computational resources are measured and monitored during an AscEE session:
\begin{itemize}
    \item \textbf{execution time}:
    is the amount of cpu time that is required for executing a session or an application call. The execution time is
    measured in \emph{AscEE clocks}. One AscEE clock is defined as 1/1000 of the amount
    of \textbf{cpu time} needed for executing a predefined standard application which is used for benchmarking a host's
    performance. In other words, by definition, the AscEE imaginary standard machine completes the standard benchmark
    in 1000 clocks.

    Optimistic sessions have a predefined \texttt{maxClocks} value which is determined by the Argennon protocol. This
    value defines a bound on the \textbf{total} AscEE clocks of the session, and no per application measurement is done.

    Monitored sessions perform per application call cpu-time measurement, and every application call during a monitored
    session has a separate \texttt{maxClocks} value. This value determines the maximum amount of time that the cpu
    can be used for executing that particular application call. It should be noted that the cpu timer of the
    application call is paused when the application makes a call to another application, and is resumed when the
    control returns. An application call
    needs at least 10 clocks and if the value of its \texttt{maxClock} is lower than this value the call will be
    considered a failed call.

    Each application call has some amount of \texttt{externalClocks}. When an application makes a request to another
    application it has to \emph{forward} a portion of its \textbf{external} clocks to the called application. This
    amount will determine the value of \texttt{maxClocks} for the called application, and is subtracted from the value
    of \texttt{externalClocks} of the caller.

    The amount of external clocks of an application
    call is defined to be \(2/3\) of its \texttt{maxClocks}. As a result, the total number of clocks of a monitored
    session is always less than \(3 \times \texttt{maxClocks}\) of the root application call. The value of
    \texttt{maxClocks} for
    the root application call is determined by the external request (i.e.\ transaction).

    \item \textbf{local memory}:
    any memory usage of an application that is not part of a heap chunk and is not part of another measured resource
    will be considered as local memory usage. Local memory is not persistent and when an application finishes serving a
    request and returns the HTTP response (i.e.\ the application call completes) its local memory is deleted.
    This resource is measured in bytes.

    Optimistic sessions measure local memory usage per session and enforce a protocol-defined cap on the total amount
    of local memory a session can use. Monitored sessions measure local memory usage per
    application call and enforce a protocol-defined cap for each application call separately. An application call
    which tries to use more local memory than the cap, fails.
    \item \textbf{heap access list}:
    every session can only access heap locations that are declared in its access list. In addition,
    resizing heap chunks can only be done in the range of the pre-declared lower bound and upper bound.
    \item \textbf{app access list}:
    a session may only make requests to applications that are declared in its application access list.
    \item \textbf{call depth}:
    during a session the number of nested application calls can not be more than a threshold. This threshold is
    determined by the Argennon protocol. It should be noted that a differed call is considered like a normal call and
    increases the call depth by one level.
    \item \textbf{differed calls}:
    every application call can have a limited number of differed calls which is determined by the protocol.
    To simplify the implementation, this limit is defined per application call. Since in Argennon the call depth is
    limited, a per-application call limit will also define an implicit limit for the total number of active differed
    calls.
    \item \textbf{virtual signatures}:
    \item \textbf{number of entrance locks}:
\end{itemize}

In Argennon, execution time and local memory are considered \emph{nondeterministic} resources. A nondeterministic
resource is a resource that can not be measured precisely and its measurement always contains a random error.
Optimistic sessions are not allowed to fail because of violating nondeterministic resource limits. As a result, the
block proposer must always choose a monitored session for a transaction that is included in the block and violates a
nondeterministic resource cap.

When a transaction fails due to the violation of a limit for a nondeterministic resource, the proposer is
required to exactly specify the application call which violates that limit in the execution session. When validators are
executing a monitored session, for each application call, they enforce considerably larger limits for
nondeterministic resources. Only in case the proposer has declared that an application call violates a limit, the
validators will enforce the actual value of the limit. This simple mechanism ensures that, with a very high
probability, validators agree with the proposer, although their measurements could be different.

>>>>

The Argennon Smart Contract Execution Environment (AscEE) is an abstract execution environment for executing Argennon
smarts contracts (a.k.a\ Argennon applications) in a secure and isolated environment. An Argennon application
essentially is an HTTP server whose state is
kept in the Argennon blockchain and its logic is described using an Argennon Standard Application Representation (ASAR).

An Argennon Standard Application Representation (ASAR) is a programming language for describing Argennon
applications, optimized
for the architecture and properties of the Argennon platform. This text based representation should be low level
enough to enable easy compilation from any high level programming language and should be high level enough to preserve
the high level information of the application logic and facilitate platform specific compiler optimization at a host
machine. In this regard, the ASAR can be considered as an Intermediate Representation (IR).

The state of an Argennon application is stored in byte addressable finite arrays of memory called
\emph{heap chunks}. An application may have several heap chunks with different sizes, and can remove or
resize its heap chunks or allocate new chunks. Every chunk belongs to exactly one application and can only be modified
by its owner. In addition to heap chunks, every application has a limited amount of non-persistent local memory for
storing temporary data.

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data for executing requests are retrieved and verified and the
helper data structures for next steps are constructed. This step is
designed in a way that can be done fully in parallel for each request without any risk of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution DAG} data
structure and in the final step, the requests are executed using this data structure.

@@

The Argennon Smart Contract Execution Environment can be seen as a machine for executing Argennon applications to
fulfill \emph{external} HTTP requests\footnote{External requests are requests that are not made by other Argennon
applications.}, produce their HTTP responses and update related heap chunks. The execution of requests can be
considered sequential\footnote{Actually requests may be executed in parallel but by performing data dependency analysis
the result is guaranteed to be identical with the sequential execution of requests.} and each request has a separate
\emph{Execution Session}. Therefore, an Execution Session is a separate session of executing application's code in
order to fulfill an External HTTP request. We call this external request the \emph{initiator} of the Execution Session.

The state of an Execution Session will be
destroyed at the end of the session and only the state of heap chunks is preserved. If a session fails and does not
complete normally, it will not have any effects on any heap chunks.

During an Execution Session an application can make \emph{internal} HTTP requests to other applications. Those
requests will not start a new Execution Session and will be executed within the current session. In AscEE making an
HTTP request to an application is similar to a function invocation, and for that reason, we also refer to them as
application calls.

\section{Memory}\label{mem}

Every Argennon application has two types of memory: local memory and heap. Local memory is not persistent and is
destroyed when the application call ends. Local memory is used for storing local variables and is not directly
addressable. Heap, on the other hand, is persistent and can be used for persisting data between application calls.
Heap is addressable and provides low level direct access. Both local memory and heap are limited, but the
AscEE does not specify any particular limits for them. When an application tries to use too much memory, that may
cause the execution session to end abruptly. In that case, the Execution Session will not have any effects on the
state of the heap.

\subsection{Heap Chunks}\label{subsec:heap}

The AscEE heap is split into chunks. Each heap chunk is a continuous finite array of bytes, has a unique identifier, and
is byte addressable. An application may have several heap chunks with different sizes and can remove or
resize its chunks or allocate new ones. Every chunk belongs to exactly one application. Only the owner application can
modify a chunk but there is no restrictions for reading a chunk\footnote{The reason behind this type of access
control design is the fact that smart contract
code is usually immutable. That means if a smart contract does not implement a
getter mechanism for some parts of its internal data, this functionality can never
be added later, and despite the internal data is publicly available, there will be no
way for other smart contracts to use this data on-chain.}.

When an application allocates a new heap chunk, the identifier of the new chunk is not generated by
the AscEE. Instead, the application can choose an identifier itself, provided it has a correct format. This
is an important feature of the AscEE heap which allows applications to use the AscEE heap as a map
data structure\footnote{also called a dictionary.}.
Since the \texttt{chunkID} is a prefix code, any application has its own identifier space, and an application
can easily find unique identifiers for its chunks.

During an Execution Session every heap chunk has an access type which may disallow certain operations. This access
type is declared by the initiator request of the Execution Session:

\begin{itemize}
    \item \texttt{check\_only}: only allows check operations. These operations query the persistence
    status of a memory location.
    \item \texttt{read\_only}: only allows read and check operations.
    \item \texttt{writable}: allows reading and writing.
    \item \texttt{additive}: only allows additive operations. By additive we mean an addition-like operator without
    overflow checking which is associative and commutative. Note that the content of these access blocks cannot be read.
\end{itemize}

\subsubsection{Chunk Resizing}\label{subsubsec:ch-resize}

At the start of executing requests of a block, a validator can consider two values for every
heap chunk, the size: \texttt{chunkSize} and a size upper bound: \texttt{sizeUpperBound}. The value of
\texttt{chunkSize} can be determined uniquely at the start of
every Execution Session, and it may be updated during the session by the owner application. On the other hand,
the value of \texttt{sizeUpperBound} proposed by the block proposer for each block and is calculated based on values
declared by requests (i.e.\ transactions) declaring chunk resizing. This value needs to be an upper bound of all the
declared values and indicates the upper bound of \texttt{chunkSize} during the execution of requests of a block.

The value of \texttt{chunkSize}, can be modified during an Execution Session. However, the new size values can only be
increasing or decreasing. More precisely, if a request declares that it wants to expand (shrink) a chunk, it can only
increase (decrease) the value of \texttt{chunkSize} and any specified value during the execution
session, needs to be greater (smaller) than the previous value of the chunk's size. Any request that wants to expand
(shrink) a chunk needs to specify a max size (min size). The value of \texttt{chunkSize} can not be set higher
(lower) than this value.

The value of \texttt{chunkSize} at the end of an Execution Session will determine if a memory location at an
offset is persistent or not: Offsets lower than the chunk size are persistent, and higher offsets are not.
Non-persistent locations will be re-initialized with zero at the start of every Execution Session.

Usually an application should not have any assumption about the content of memory locations that are outside the chunk.
While these locations are zero initialized at the start of every Execution Session, it should be noted that multiple
invocations of an application may occur in a single Execution Session, and if one of them modifies a location outside
the chunk, the changes can be seen by next invocations.

There is no way for an application to query \texttt{sizeUpperBound}. As a result, for an application,
accessing offsets higher than \texttt{chunkSize} results in undefined behaviour, while the behaviour is well-defined
in the view of validators.
This enables validators to determine the validity of an offset at the start of the block validation in a parallelized
preprocessing phase without actually executing requests.

@@

@@

\section{Authorization}\label{sec:auth}

In blockchain applications, we usually need to authorize certain operations. For example, for sending an asset
from a user to another user, we need to make sure that the sender has authorized that operation.

The AscEE uses \emph{Authenticated Message Passing} for authorizing operations. In this method, every Execution
Session has a set of authenticated messages, and those messages are \textbf{explicitly} passed in requests to
applications for authorizing operations. These messages act exactly like digital signatures and applications can
ensure that they are issued by their claimed issuer accounts. The only difference is that the process of
message authentication is performed by the AscEE internally and an application does not explicitly verify cryptographic
signatures.

Each Execution Session has a list of authenticated messages. Each authenticated message has an index which will be
used for passing the message to an application as a request parameter. The AscEE uses cryptographic signatures to
authenticate messages for user accounts. The signatures are validated in parallel during the
preprocessing step of the block validation, and any type of cryptographic signature scheme can be used.

Also, applications can use built-in functions of the AscEE to generate authenticated messages in run-time.
This enables an application to authorize operations for another application even if it is not calling that
application directly.

In addition to authenticated messages, the AscEE provides a set of
cryptographic functions for validating signatures and calculating cryptographic entities. By using these functions and
passing cryptographic signatures as parameters to methods, a programmer, having users' public keys, can implement
the required logic for authorizing operations.

Authorizing operations by Authenticated Message Passing and explicit signatures eliminates the need for approval
mechanisms or call back patterns in Argennon.\footnote{The AscEE has no instructions for issuing cryptographic
signatures.}

@@

The AscEE provides optional low level reentrancy protection by providing low
level \emph{entrance locks}. When an application acquires an entrance lock it cannot acquire that lock again and trying
to do so will result in a revert. The entrance lock of an application will be released when the application explicitly
releases its lock or when the call that has acquired that lock completes.

@@

### 2022-09-02 tex/sections/elements.tex
Add the APM
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

>>>>

\section{Resource Management}\label{sec:res-man}

Completing an Execution Session requires computational resources. The amount of resources used by an Execution Session
should be monitored and managed, otherwise a malicious user would be able to easily spam and exhaust resources of the
execution environment.

In most consensus protocols, we can assume that the block proposer has enough incentive to filter out transactions
that spam run-time resources. Here by a run-time resource, we mean a resource that at run-time, a limited amount
of it is available, but its surplus can not be stored for later use. Execution time and local memory are
examples of such a resource but permanent storage is not.

If a proposed block contains many transactions which need a lot of run-time resources, validators would not
be able to validate all transactions in a timely manner. Consequently, they may decide to reject the block or if they
spend enough resources, the confirmation of that block could take more than usual. Longer block time is not
favoured by block proposers, because it means less throughput of the system which usually means less overall rewards
for them. In the Argennon protocol the management of run-time resources, is left to the block proposer.

Resource usage can be measured per session or per application call. Obviously per session measurement is
easier and more efficient. However, when we measure resources per session if
a session violates its resource caps, determining the point of failure may require precise and error-free resource
measurement. For example, assume that a session containing an application call
violates a 2 milliseconds execution time cap. If in the caller's code, the call happens exactly after 2 milliseconds,
a small fluctuation in the execution time measurement can
change the point of failure between the called and the caller application. Note that for implementing optional
decoupling principle in Argennon, we need to determine the
exact application call which has failed in a call chain, and this fluctuation introduces a nondeterministic
behaviour which could make block validation impossible. That's why we need per application call
resource management sometimes. If we define the resource caps per application call and
perform our measurements for each application call separately, by using caps that are larger than the measurement
error, errors in the measurements would not change the point of failure in the call chain.

The AscEE has two types of execution sessions: \emph{optimistic} and \emph{monitored}. Resource usage of an optimistic
session is always measured per session and \textbf{default} pre-defined resource caps are used. On the other hand, for a
monitored session, resources that can not be measured precisely are measured per application call and their caps are
determined per application call by the external HTTP request (i.e.\ transaction). The block proposer decides the
type of the Execution Session for each transaction.

Different computational resources are measured and monitored during an AscEE session:
\begin{itemize}
    \item \textbf{execution time}:
    is the amount of cpu time that is required for executing a session or an application call. The execution time is
    measured in \emph{AscEE clocks}. One AscEE clock is defined as 1/1000 of the amount
    of \textbf{cpu time} needed for executing a predefined standard application which is used for benchmarking a host's
    performance. In other words, by definition, the AscEE imaginary standard machine completes the standard benchmark
    in 1000 clocks.

    Optimistic sessions have a predefined \texttt{maxClocks} value which is determined by the Argennon protocol. This
    value defines a bound on the \textbf{total} AscEE clocks of the session, and no per application measurement is done.

    Monitored sessions perform per application call cpu-time measurement, and every application call during a monitored
    session has a separate \texttt{maxClocks} value. This value determines the maximum amount of time that the cpu
    can be used for executing that particular application call. It should be noted that the cpu timer of the
    application call is paused when the application makes a call to another application, and is resumed when the
    control returns. An application call
    needs at least 10 clocks and if the value of its \texttt{maxClock} is lower than this value the call will be
    considered a failed call.

    Each application call has some amount of \texttt{externalClocks}. When an application makes a request to another
    application it has to \emph{forward} a portion of its \textbf{external} clocks to the called application. This
    amount will determine the value of \texttt{maxClocks} for the called application, and is subtracted from the value
    of \texttt{externalClocks} of the caller.

    The amount of external clocks of an application
    call is defined to be \(2/3\) of its \texttt{maxClocks}. As a result, the total number of clocks of a monitored
    session is always less than \(3 \times \texttt{maxClocks}\) of the root application call. The value of
    \texttt{maxClocks} for
    the root application call is determined by the external request (i.e.\ transaction).

    \item \textbf{local memory}:
    any memory usage of an application that is not part of a heap chunk and is not part of another measured resource
    will be considered as local memory usage. Local memory is not persistent and when an application finishes serving a
    request and returns the HTTP response (i.e.\ the application call completes) its local memory is deleted.
    This resource is measured in bytes.

    Optimistic sessions measure local memory usage per session and enforce a protocol-defined cap on the total amount
    of local memory a session can use. Monitored sessions measure local memory usage per
    application call and enforce a protocol-defined cap for each application call separately. An application call
    which tries to use more local memory than the cap, fails.
    \item \textbf{heap access list}:
    every session can only access heap locations that are declared in its access list. In addition,
    resizing heap chunks can only be done in the range of the pre-declared lower bound and upper bound.
    \item \textbf{app access list}:
    a session may only make requests to applications that are declared in its application access list.
    \item \textbf{call depth}:
    during a session the number of nested application calls can not be more than a threshold. This threshold is
    determined by the Argennon protocol. It should be noted that a differed call is considered like a normal call and
    increases the call depth by one level.
    \item \textbf{differed calls}:
    every application call can have a limited number of differed calls which is determined by the protocol.
    To simplify the implementation, this limit is defined per application call. Since in Argennon the call depth is
    limited, a per-application call limit will also define an implicit limit for the total number of active differed
    calls.
    \item \textbf{virtual signatures}:
    \item \textbf{number of entrance locks}:
\end{itemize}

In Argennon, execution time and local memory are considered \emph{nondeterministic} resources. A nondeterministic
resource is a resource that can not be measured precisely and its measurement always contains a random error.
Optimistic sessions are not allowed to fail because of violating nondeterministic resource limits. As a result, the
block proposer must always choose a monitored session for a transaction that is included in the block and violates a
nondeterministic resource cap.

When a transaction fails due to the violation of a limit for a nondeterministic resource, the proposer is
required to exactly specify the application call which violates that limit in the Execution Session. When validators are
executing a monitored session, for each application call, they enforce considerably larger limits for
nondeterministic resources. Only in case the proposer has declared that an application call violates a limit, the
validators will enforce the actual value of the limit. This simple mechanism ensures that, with a very high
probability, validators agree with the proposer, although their measurements could be different.

### 2022-09-02 tex/sections/incentive.tex
Add the APM
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

For our incentive mechanism, we require that every time a validator receives a storage page from a PVC, after
validating the data, he gives a receipt to the PVC server. In this receipt the validator signs the
following information:

>>>>

For our incentive mechanism, we require that every time a validator receives a storage page from a PVC, after
validating the data, he give a receipt to the PVC server. In this receipt the validator signs the
following information:

### 2022-09-02 tex/sections/intro.tex
Add the APM
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

On the blockchain, Argennon applications (i.e smart contracts) are stored in a high level text based language, called
the Argennon Standard Application Representation (ASAR). The ASAR is intended for preserving the
high level information of the application logic to facilitate platform specific compiler optimization at a host
machine. This enables delegates to compile and optimize Argennon applications for their specific hardware platforms
and execute applications efficiently, ensuring the state transition can be found as fast as possible. Moreover,
validators by using a special compiler, generate arithmetization of this language and use it for verifying CI proofs.

>>>>

On the blockchain, Argennon applications (i.e smart contracts) are stored in a high level text based language, called
the Argennon Standard Application Representation (ASAR). The ASAR is intended for preserving the
high level information of the application logic to facilitate platform specific compiler optimization at a host
machine. This enables delegates to compile and optimize Argennon applications for their specific hardware platforms
and execute applications efficiently, ensuring the state transition can be found as fast as possible.

In addition to the ASAR, on the blockchain an Argennon application is stored in the Argennon Prover Machine (APM) code.
This code is used by validators for CI proof verification. The Argennon Prover Machine is a virtual
machine tailored for efficient verification of AscEE computations by
argument systems. The APM has a minimal RISC architecture with a very compact instruction set. This ensures that
its transition function has an efficient circuit complexity.
